Instructions for running Shiny server to explore results of Gaussian mean estimation experiments

### 2018-12-07 analysis/gauss_shiny_setup.Rmd
wflow_publish("gauss_shiny_setup.Rmd")

*Briefly explain here what this R Markdown document is for.*

@@

```{r load-pkgs, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(rmarkdown)
```

NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`

The following code generates an RShiny app which displays boxplots of
MISEs from the full simulation study comparing SMASH to other
wavelet-based methods for denoising Gaussian data. As mentioned in the
companion paper, the results for a variety of test functions (both
mean and variance functions) and 2 signal-to-noise ratios (SNRs), 1
and 3, are presented here.

>>>>

Here we give instructions for starting the Shiny server which will
create an interactive plot from the results of the Gaussian mean
estimation simulation study.

@@

First, you need make sure that the following R packages are installed
on your computer: dplyr, ggplot2, cowplot, shiny and rmarkdown. See
the "Session Info" at the bottom for the versions of the R packages we
used.  Once you have installed these packages, run this code to verify
that the packages are installed successfully:

```{r load-pkgs, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(cowplot)
library(shiny)
library(rmarkdown)
```

Now you are ready to create the Shiny server with this command:

```{r launch-shiny, eval=FALSE}
rmarkdown::run("../shiny/gauss_shiny.Rmd")
```

The interactive plot will be launched in your Web browser, or in an
RStudio panel, depending on whether you are using R or RStudio.
